`r params$doc_title`

### 2023-03-13 scripts/MSc.Rmd
added summary plots faceted by scenario

if (SAVE.files ==TRUE ){
  filenamefig00_b <- paste0("../output/plots/", Sys.Date(), "_explained_var_X_new_sample_size_dep.png")
  ggsave(filename = filenamefig00_b, plot = fig00_b, 
       width = 10, height = 6, 
       units = "in"  # default
       )
}

@@

if (SAVE.files ==TRUE ){
  filenamefig01_b <- paste0("../output/plots/", Sys.Date(), "_figure01_new_PVE_X_formula.png")
  ggsave(filename = filenamefig01_b, plot = fig01b.update, 
         width = 10, height = 6, 
         units = "in"  # default
         )
}
```

@@

# SAVE
if (SAVE.files ==TRUE ){
  filenamefig02 <- paste0("../output/plots/", Sys.Date(), "_figure02.png")
  ggsave(filename = filenamefig02, plot = fig02.update)
}
```

@@

# final_plot1.arrange   # OLD
final_plot1.arrange2   # use this!
if (SAVE.files ==TRUE ){
  filename_final_plot1 <- paste0("../output/plots/", Sys.Date(), "_final_plot1.arrange_OLD.png")
  filename_final_plot1b <- paste0("../output/plots/", Sys.Date(), "_final_plot1b.arrange_NEW.png")

  ggsave(filename = filename_final_plot1, plot = final_plot1.arrange, 
           width = 14, height = 10, 
           units = "in"  # default
           )
  ggsave(filename = filename_final_plot1b, plot = final_plot1.arrange2, 
           width = 14, height = 10, 
           units = "in"  # default
           )
}
```

@@

# SAVE
if (SAVE.files ==TRUE ){
  filename.mr.scatter.gsd <- paste0("../output/plots/", Sys.Date(), "_figure_mrscatter_gsd.png")
  ggsave(filename = filename.mr.scatter.gsd, plot = p1.gsd, 
           width = 10, height = 6, 
           units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.forest.gsd <- paste0("../output/plots/", Sys.Date(), "_figure_mrforest_GSD.png")
  ggsave(filename = filename.mr.forest.gsd, plot = p2.gsd, 
         width = 5, 
         height = 24, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.funnel.gsd <- paste0("../output/plots/", Sys.Date(), "_figure_mrfunnel_gsd.png")
  ggsave(filename = filename.mr.funnel.gsd, plot = p4.gsd, 
         width = 8, 
         height = 4, 
         units = "in"  # default
           )
}

@@

# SAVE
if (SAVE.files ==TRUE ){
  filename.mr.scatter <- paste0("../output/plots/", Sys.Date(), "_figure_mrscatter.png")
  ggsave(filename = filename.mr.scatter, plot = p1[[1]], 
           #width = 10, height = 6, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.forest <- paste0("../output/plots/", Sys.Date(), "_figure_mrforest_GBC.png")
  ggsave(filename = filename.mr.forest, plot = p2[[1]], 
         width = 5, 
         height = 24, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.funnel.gbc <- paste0("../output/plots/", Sys.Date(), "_figure_mrfunnel_gbc.png")
  ggsave(filename = filename.mr.funnel.gbc, plot = p4, 
         width = 8, 
         height = 4, 
         units = "in"  # default
           )
}
```

@@

if (SAVE.files ==TRUE ){
  filename_pveplot_sim <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_pve.png")
  ggsave(filename = filename_pveplot_sim, plot = plot_pve_simulated, 
         width = 10, height = 6, 
         units = "in"  # default
         )
}
```

@@

if (SAVE.files ==TRUE ){
  filename_pveplot_sim.raincloud <- paste0("../output/plots/", Sys.Date(), "_figure_simplot_pve_raincloud.png")
  ggsave(filename = filename_pveplot_sim.raincloud, plot = plot_pve_simulated.raincloud, 
         width = 10, height = 6, 
         units = "in"  # default
         )
}
```

@@

# coverage bias eliminated
coverage_bias_eliminated <- function(thetaobs, thetaobs_se, ...) {
  lower_ci <- thetaobs - 1.96*thetaobs_se
  upper_ci <- thetaobs + 1.96*thetaobs_se
  mean_thetaobs <- mean(thetaobs)
  coverage_bias_eliminated <- mean(lower_ci <= mean_thetaobs & upper_ci >=mean_thetaobs)
  return(coverage_bias_eliminated)
}
# type1error
type1error <- function(pvals) sum(pvals<=0.05)/length(pvals)  # no causal_effect

@@

```{r store-performance-metrics-csv}
## GSD  we loop in the next section and save the files there with all references!
# filename_IVW_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_IVW_GSD_performance_metrics_NSIM_", nsim, ".csv")
# filename_MODE_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_MODE_GSD_performance_metrics_NSIM_", nsim, ".csv")
# filename_CONMIX_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_CONMIX_GSD_performance_metrics_NSIM_", nsim, ".csv")
# filename_MRMIX_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_MRMIX_GSD_performance_metrics_NSIM_", nsim, ".csv")
# #5
# filename_MEDIAN_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_MEDIAN_GSD_performance_metrics_NSIM_", nsim, ".csv")
# #6
# filename_EGGER_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_EGGER_GSD_performance_metrics_NSIM_", nsim, ".csv")
# #7
# filename_ROBUST_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_ROBUST_GSD_performance_metrics_NSIM_", nsim, ".csv")
# #8
# filename_PRESSO_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_PRESSO_GSD_performance_metrics_NSIM_", nsim, ".csv")
# #9
# filename_RAPS_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_RAPS_GSD_performance_metrics_NSIM_", nsim, ".csv")
# #10
# filename_LASSO_GSD_performance_metrics <- paste0("../output/performance_metrics/", 
#                                                Sys.Date(), "_LASSO_GSD_performance_metrics_NSIM_", nsim, ".csv")
# write.csv2(x = IVW_GSD_performance_metrics, file = filename_IVW_GSD_performance_metrics)
# write.csv2(x = MODE_GSD_performance_metrics, file = filename_MODE_GSD_performance_metrics)
# write.csv2(x = CONMIX_GSD_performance_metrics, file = filename_CONMIX_GSD_performance_metrics)
# write.csv2(x = MRMIX_GSD_performance_metrics, file = filename_MRMIX_GSD_performance_metrics)
# #5
# write.csv2(x = MEDIAN_GSD_performance_metrics, file = filename_MEDIAN_GSD_performance_metrics)
# #6
# write.csv2(x = EGGER_GSD_performance_metrics, file = filename_EGGER_GSD_performance_metrics)
# #7
# write.csv2(x = ROBUST_GSD_performance_metrics, file = filename_ROBUST_GSD_performance_metrics)
# #8
# write.csv2(x = PRESSO_GSD_performance_metrics, file = filename_PRESSO_GSD_performance_metrics)
# #9
# write.csv2(x = RAPS_GSD_performance_metrics, file = filename_RAPS_GSD_performance_metrics)
# #10
# write.csv2(x = LASSO_GSD_performance_metrics, file = filename_LASSO_GSD_performance_metrics)
```

```{r}
#s1 <- simsum(data = est_sim, estvarname = "IVW_theta_sim_BMI_GSD_40000", se = "IVW_theta_se_sim_BMI_GSD_40000", true = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "IVW"] )

## stats param
# • nsim,the number of replications with non-missing point estimates and standard error.
# • thetamean, average point estimate.
# • thetamedian, median point estimate.
# • se2mean, average variance.
# • se2median, median variance.
# • bias, bias in point estimate.
# • empse, empirical standard error.
# • mse, mean squared error.
# • relprec, percentage gain in precision relative to the reference method.
# • modelse, model-based standard error.
# • relerror, relative percentage error in standard error.
# • cover, coverage of a nominal level\
# • becover, bias corrected coverage of a nominal level\
# • power, power of a (1 - level)\

#statsparam <- c("nsim", "thetamean", "se2mean", "bias", "empse", "mse", "cover", "becover", "power")
#simsum_summary <- summary(s1, stats = statsparam)
```

@@

if (SAVE.files ==TRUE ){
  filename_GSD_simplot_thetas_arrange <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_thetas_NSIM_", nsim,".png")
  ggsave(filename = filename_GSD_simplot_thetas_arrange, plot = GSD_simplot_thetas_arrange, 
         width = 10, height = 22, 
         units = "in"  # default
         )
}
```

@@

if (SAVE.files ==TRUE ){
  filename_simplot_bias_mse <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_bias_mse_NSIM_", nsim, ".png")
  ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot_GSD, 
         width = 7, height = 12, 
         units = "in"  # default
         )
}
```

@@

  # STORE
  if (SAVE.files ==TRUE ){
    filename.IVW_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_IVW_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = IVW_GSD_performance_metrics, file = filename.IVW_table.performance)
    filename.MODE_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_MODE_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = MODE_GSD_performance_metrics, file = filename.MODE_table.performance)
    filename.CONMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_CONMIX_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = CONMIX_GSD_performance_metrics, file = filename.CONMIX_table.performance)
    filename.MRMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_MRMIX_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = MRMIX_GSD_performance_metrics, file = filename.MRMIX_table.performance)
    #5
    filename.MEDIAN_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_MEDIAN_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = MEDIAN_GSD_performance_metrics, file = filename.MEDIAN_table.performance)
    #6
    filename.EGGER_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_EGGER_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = EGGER_GSD_performance_metrics, file = filename.EGGER_table.performance)
    #7
    filename.ROBUST_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_ROBUST_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = ROBUST_GSD_performance_metrics, file = filename.ROBUST_table.performance)
    #8
    filename.PRESSO_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_PRESSO_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = PRESSO_GSD_performance_metrics, file = filename.PRESSO_table.performance)
    #9
    filename.RAPS_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_RAPS_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = RAPS_GSD_performance_metrics, file = filename.RAPS_table.performance)
    #10
    filename.LASSO_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                        "_LASSO_GSD_performance_metrics_TRUE_EST_", 
                                        selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
    write.csv2(x = LASSO_GSD_performance_metrics, file = filename.LASSO_table.performance)
  }

@@

  ####-------------
  # SAVE  --------------------------------
  if (SAVE.files ==TRUE ){
    #1
    filename_IVW_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_IVW_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
    ggsave(filename = filename_IVW_GSD_simplot_thetas, plot = IVW_GSD_simplot_thetas, 
           width = 15, height = 6, 
           units = "in"  # default
           )
    #2
    filename_MODE_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MODE_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
    ggsave(filename = filename_MODE_GSD_simplot_thetas, plot = MODE_GSD_simplot_thetas, 
           width = 15, height = 6, 
           units = "in"  # default
           )
    #3
    filename_CONMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_CONMIX_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
    ggsave(filename = filename_CONMIX_GSD_simplot_thetas, plot = CONMIX_GSD_simplot_thetas, 
           width = 15, height = 6, 
           units = "in"  # default
           )
    #4
    filename_MRMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MRMIX_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
    ggsave(filename = filename_MRMIX_GSD_simplot_thetas, plot = MRMIX_GSD_simplot_thetas, 
           width = 15, height = 6, 
           units = "in"  # default
           )
    #5
    filename_MEDIAN_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MEDIAN_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
    ggsave(filename = filename_MEDIAN_GSD_simplot_thetas, plot = MEDIAN_GSD_simplot_thetas, 
           width = 15, height = 6, 
           units = "in"  # default
           )
    #6
    filename_EGGER_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_EGGER_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
    ggsave(filename = filename_EGGER_GSD_simplot_thetas, plot = EGGER_GSD_simplot_thetas, 
           width = 15, height = 6, 
           units = "in"  # default
           )
    #7
    filename_ROBUST_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_ROBUST_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
    ggsave(filename = filename_ROBUST_GSD_simplot_thetas, plot = ROBUST_GSD_simplot_thetas, 
           width = 15, height = 6, 
           units = "in"  # default
           )
    #8
    filename_PRESSO_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_PRESSO_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
    ggsave(filename = filename_PRESSO_GSD_simplot_thetas, plot = PRESSO_GSD_simplot_thetas, 
           width = 15, height = 6, 
           units = "in"  # default
           )
    #9
    filename_RAPS_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_RAPS_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
    ggsave(filename = filename_RAPS_GSD_simplot_thetas, plot = RAPS_GSD_simplot_thetas, 
           width = 15, height = 6, 
           units = "in"  # default
           )
    #10
    filename_LASSO_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_LASSO_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
    ggsave(filename = filename_LASSO_GSD_simplot_thetas, plot = LASSO_GSD_simplot_thetas, 
           width = 15, height = 6, 
           units = "in"  # default
           )
  }

@@

  if (SAVE.files ==TRUE ){
    filename_GSD_simplot_thetas_arrange <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
    ggsave(filename = filename_GSD_simplot_thetas_arrange, plot = GSD_simplot_thetas_arrange, 
           width = 10, height = 38, 
           units = "in"  # default
           )
  }

@@

  if (SAVE.files ==TRUE ){
    filename_simplot_bias_mse <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_bias_mse_REF_METHOD_", selected_true_methods[true_method], "_NSIM_",nsim, ".png")
    ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot_GSD, 
           width = 7, height = 24, 
           units = "in"  # default
           )
  }
}

@@

    # STORE
    if (SAVE.files ==TRUE ){
      filename.IVW_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
                                          "_IVW_GSD_performance_metrics_TRUE_EST_", 
                                          "_GenArch_", name_GenArch,
                                          "_NSIM_", nsim, ".csv")
      write.csv2(x = IVW_GSD_performance_metrics, file = filename.IVW_table.performance)

>>>>

if (SAVE.files ==TRUE ){
  filenamefig00_b <- paste0("../output/plots/pve/", Sys.Date(), "_explained_var_X_new_sample_size_dep.svg")
  ggsave(filename = filenamefig00_b, plot = fig00_b, 
       width = 10, height = 6, 
       units = "in"  # default
       )
}

@@

# if (SAVE.files ==TRUE ){
#   filenamefig01_b <- paste0("../output/plots/", Sys.Date(), "_figure01_new_PVE_X_formula.png")
#   ggsave(filename = filenamefig01_b, plot = fig01b.update, 
#          width = 10, height = 6, 
#          units = "in"  # default
#          )
# }
```

@@

# # SAVE
# if (SAVE.files ==TRUE ){
#   filenamefig02 <- paste0("../output/plots/", Sys.Date(), "_figure02.png")
#   ggsave(filename = filenamefig02, plot = fig02.update)
# }
```

@@

# final_plot1.arrange   # OLD
final_plot1.arrange2   # use this!
if (SAVE.files ==TRUE ){
  filename_final_plot1 <- paste0("../output/plots/pve/", Sys.Date(), "_final_plot1.arrange_OLD.svg")
  filename_final_plot1b <- paste0("../output/plots/pve/", Sys.Date(), "_final_plot1b.arrange_NEW.svg")

  # ggsave(filename = filename_final_plot1, plot = final_plot1.arrange, 
  #          width = 14, height = 10, 
  #          units = "in"  # default
  #          )
  ggsave(filename = filename_final_plot1b, plot = final_plot1.arrange2, 
           width = 14, height = 10, 
           units = "in"  # default
           )
}
```

@@

# SAVE
if (SAVE.files ==TRUE ){
  filename.mr.scatter.gsd <- paste0("../output/plots/mr-analysis/", Sys.Date(), "_figure_mrscatter_gsd.svg")
  ggsave(filename = filename.mr.scatter.gsd, plot = p1.gsd, 
           width = 10, height = 6, 
           units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.forest.gsd <- paste0("../output/plots/mr-analysis/", Sys.Date(), "_figure_mrforest_GSD.svg")
  ggsave(filename = filename.mr.forest.gsd, plot = p2.gsd, 
         width = 5, 
         height = 24, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.funnel.gsd <- paste0("../output/plots/mr-analysis/", Sys.Date(), "_figure_mrfunnel_gsd.svg")
  ggsave(filename = filename.mr.funnel.gsd, plot = p4.gsd, 
         width = 8, 
         height = 4, 
         units = "in"  # default
           )
}

@@

# SAVE
if (SAVE.files ==TRUE ){
  filename.mr.scatter <- paste0("../output/plots/mr-analysis/", Sys.Date(), "_figure_mrscatter.svg")
  ggsave(filename = filename.mr.scatter, plot = p1[[1]], 
           #width = 10, height = 6, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.forest <- paste0("../output/plots/mr-analysis/", Sys.Date(), "_figure_mrforest_GBC.svg")
  ggsave(filename = filename.mr.forest, plot = p2[[1]], 
         width = 5, 
         height = 24, 
           #units = "in"  # default
           )
}
```

@@

#SAVE
if (SAVE.files ==TRUE ){
  filename.mr.funnel.gbc <- paste0("../output/plots/mr-analysis/", Sys.Date(), "_figure_mrfunnel_gbc.svg")
  ggsave(filename = filename.mr.funnel.gbc, plot = p4, 
         width = 8, 
         height = 4, 
         units = "in"  # default
           )
}
```

@@

# if (SAVE.files ==TRUE ){
#   filename_pveplot_sim <- paste0("../output/plots/pve/", Sys.Date(), "_figure_simplot_pve.png")
#   ggsave(filename = filename_pveplot_sim, plot = plot_pve_simulated, 
#          width = 10, height = 6, 
#          units = "in"  # default
#          )
# }
```

@@

if (SAVE.files ==TRUE ){
  filename_pveplot_sim.raincloud <- paste0("../output/plots/pve/", Sys.Date(), "_figure_simplot_pve_raincloud.svg")
  ggsave(filename = filename_pveplot_sim.raincloud, plot = plot_pve_simulated.raincloud, 
         width = 10, height = 6, 
         units = "in"  # default
         )
}
```

@@

# coverage bias eliminated
coverage_bias_eliminated <- function(thetaobs, thetaobs_se, ...) {
  lower_ci <- thetaobs - 1.96*thetaobs_se
  upper_ci <- thetaobs + 1.96*thetaobs_se
  mean_thetaobs <- mean(thetaobs)
  coverage_bias_eliminated <- mean(lower_ci <= mean_thetaobs & upper_ci >=mean_thetaobs)
  return(coverage_bias_eliminated)
}
# type1error
type1error <- function(pvals) sum(pvals<=0.05)/length(pvals)  # no causal_effect detected

@@

```{r}
library(rsimsum)
s1 <- simsum(data = est_sim, estvarname = "IVW_theta_sim_BMI_GSD_150000", se = "IVW_theta_se_sim_BMI_GSD_150000", true = est.bmi.gsd$estimate[est.bmi.gsd$mr_methods == "IVW"] )

## stats param
# • nsim,the number of replications with non-missing point estimates and standard error.
# • thetamean, average point estimate.
# • thetamedian, median point estimate.
# • se2mean, average variance.
# • se2median, median variance.
# • bias, bias in point estimate.
# • empse, empirical standard error.
# • mse, mean squared error.
# • relprec, percentage gain in precision relative to the reference method.
# • modelse, model-based standard error.
# • relerror, relative percentage error in standard error.
# • cover, coverage of a nominal level\
# • becover, bias corrected coverage of a nominal level\
# • power, power of a (1 - level)\
statsparam <- c("nsim", "thetamean", "se2mean", "bias", "empse", "mse", "cover", "becover", "power")
simsum_summary <- summary(s1, stats = statsparam)
```

@@

# if (SAVE.files ==TRUE ){
#   filename_GSD_simplot_thetas_arrange <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_thetas_NSIM_", nsim,".png")
#   ggsave(filename = filename_GSD_simplot_thetas_arrange, plot = GSD_simplot_thetas_arrange, 
#          width = 10, height = 22, 
#          units = "in"  # default
#          )
# }
```

@@

# if (SAVE.files ==TRUE ){
#   filename_simplot_bias_mse <- paste0("../output/plots/", Sys.Date(), "_GSD_simplot_bias_mse_NSIM_", nsim, ".png")
#   ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot_GSD, 
#          width = 7, height = 12, 
#          units = "in"  # default
#          )
# }
```

@@

  # # STORE
  # if (SAVE.files ==TRUE ){
  #   filename.IVW_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_IVW_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = IVW_GSD_performance_metrics, file = filename.IVW_table.performance)
  #   filename.MODE_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_MODE_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = MODE_GSD_performance_metrics, file = filename.MODE_table.performance)
  #   filename.CONMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_CONMIX_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = CONMIX_GSD_performance_metrics, file = filename.CONMIX_table.performance)
  #   filename.MRMIX_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_MRMIX_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = MRMIX_GSD_performance_metrics, file = filename.MRMIX_table.performance)
  #   #5
  #   filename.MEDIAN_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_MEDIAN_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = MEDIAN_GSD_performance_metrics, file = filename.MEDIAN_table.performance)
  #   #6
  #   filename.EGGER_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_EGGER_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = EGGER_GSD_performance_metrics, file = filename.EGGER_table.performance)
  #   #7
  #   filename.ROBUST_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_ROBUST_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = ROBUST_GSD_performance_metrics, file = filename.ROBUST_table.performance)
  #   #8
  #   filename.PRESSO_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_PRESSO_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = PRESSO_GSD_performance_metrics, file = filename.PRESSO_table.performance)
  #   #9
  #   filename.RAPS_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_RAPS_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = RAPS_GSD_performance_metrics, file = filename.RAPS_table.performance)
  #   #10
  #   filename.LASSO_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
  #                                       "_LASSO_GSD_performance_metrics_TRUE_EST_", 
  #                                       selected_true_methods[true_method], "_NSIM_", nsim, ".csv")
  #   write.csv2(x = LASSO_GSD_performance_metrics, file = filename.LASSO_table.performance)
  # }

@@

  # ####-------------
  # # SAVE  --------------------------------
  # if (SAVE.files ==TRUE ){
  #   #1
  #   filename_IVW_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_IVW_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_IVW_GSD_simplot_thetas, plot = IVW_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #2
  #   filename_MODE_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MODE_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_MODE_GSD_simplot_thetas, plot = MODE_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #3
  #   filename_CONMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_CONMIX_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_CONMIX_GSD_simplot_thetas, plot = CONMIX_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #4
  #   filename_MRMIX_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MRMIX_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_MRMIX_GSD_simplot_thetas, plot = MRMIX_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #5
  #   filename_MEDIAN_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_MEDIAN_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_MEDIAN_GSD_simplot_thetas, plot = MEDIAN_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #6
  #   filename_EGGER_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_EGGER_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_EGGER_GSD_simplot_thetas, plot = EGGER_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #7
  #   filename_ROBUST_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_ROBUST_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_ROBUST_GSD_simplot_thetas, plot = ROBUST_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #8
  #   filename_PRESSO_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_PRESSO_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_PRESSO_GSD_simplot_thetas, plot = PRESSO_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #9
  #   filename_RAPS_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_RAPS_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_RAPS_GSD_simplot_thetas, plot = RAPS_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  #   #10
  #   filename_LASSO_GSD_simplot_thetas <- paste0("../output/plots/", Sys.Date(), "_LASSO_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".png")
  #   ggsave(filename = filename_LASSO_GSD_simplot_thetas, plot = LASSO_GSD_simplot_thetas, 
  #          width = 15, height = 6, 
  #          units = "in"  # default
  #          )
  # }

@@

  if (SAVE.files ==TRUE ){
    filename_GSD_simplot_thetas_arrange <- paste0("../output/plots/theta_sims/", Sys.Date(), "_GSD_simplot_thetas_REF_METHOD_", selected_true_methods[true_method], "_NSIM_", nsim,".svg")
    ggsave(filename = filename_GSD_simplot_thetas_arrange, plot = GSD_simplot_thetas_arrange, 
           width = 10, height = 38, 
           units = "in"  # default
           )
  }

@@

  if (SAVE.files ==TRUE ){
    filename_simplot_bias_mse <- paste0("../output/plots/bias-mse/", Sys.Date(), "_GSD_simplot_bias_mse_REF_METHOD_", selected_true_methods[true_method], "_NSIM_",nsim, ".svg")
    ggsave(filename = filename_simplot_bias_mse, plot = bias_mse_plot_GSD, 
           width = 7, height = 24, 
           units = "in"  # default
           )
  }
}

@@

    # # STORE
    # if (SAVE.files ==TRUE ){
    #   filename.IVW_table.performance <- paste0("../output/performance_metrics/", Sys.Date(), 
    #                                       "_IVW_GSD_performance_metrics_TRUE_EST_", 
    #                                       selected_true_methods[true_method], 
    #                                       "_GenArch_", name_GenArch,
    #                                       "_NSIM_", nsim, ".csv")
